### 2018-02-20 submission/supplemental.Rmd
remove what the taq component
update with bringing the lead to the fore
update supplemental table headings

# What the Taq? The Influence of Different Hi-Fidelity Taq Polymerase on 16S rRNA Sequencing

@@

**Table S1: ANOVA Results of Number of OTUs Differences between HiFi Taq in Fecal Samples**

@@

**Table S2: Tukey Post-Hoc Results of Number of OTUs Differences between HiFi Taq in Fecal Samples**

@@

**Table S3: ANOVA Results of Number of OTUs Differences between HiFi Taq in Mock Samples**

@@

**Table S4: Tukey Post-Hoc Results of Number of OTUs Differences between HiFi Taq in Mock Samples**

@@

**Table S5: Kruskal-Wallis Results of Per Base Error Rate Differences between HiFi Taq in Mock Samples**

@@

**Table S6: Dunn's Post-Hoc Results of Per Base Error Rate between HiFi Taq in Mock Samples**

@@

**Table S7: Kruskal-Wallis Results of Sequences with Error Differences between HiFi Taq in Mock Samples**

@@

**Table S8: Dunn's Post-Hoc Results of Sequences with Error Differences between HiFi Taq in Mock Samples**

@@

**Table S9: Kruskal-Wallis Results of Chimera Differences between HiFi Taq in Mock Samples**

@@

**Table S10: Dunn's Post-Hoc Results of Chimera Differences between HiFi Taq in Mock Samples**

>>>>

# The Influence of Different High Fidelity DNA Polymerase on 16S rRNA Sequencing

@@

**Table S1: ANOVA Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal Samples**

@@

**Table S2: Tukey Post-Hoc Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal Samples**

@@

**Table S3: ANOVA Results of Differences in Number of OTUs between HiFi DNA Polymerases in Mock Samples**

@@

**Table S4: Tukey Post-Hoc Results of Differences in Number of OTUs between HiFi DNA Polymerases in Mock Samples**

@@

**Table S5: Kruskal-Wallis Results of Differences in Per Base Error Rate between HiFi DNA Polymerases in Mock Samples**

@@

**Table S6: Dunn's Post-Hoc Results of Differences in Per Base Error Rate between HiFi DNA Polymerases in Mock Samples**

@@

**Table S7: Kruskal-Wallis Results of Differences in Sequences with Error between HiFi DNA Polymerases in Mock Samples**

@@

**Table S8: Dunn's Post-Hoc Results of Differences in Sequences with Error between HiFi DNA Polymerases in Mock Samples**

@@

**Table S9: Kruskal-Wallis Results of Differences in Chimera Prevalence between HiFi DNA Polymerases in Mock Samples**

@@

**Table S10: Dunn's Post-Hoc Results of Differences in Chimera Prevalence between HiFi DNA Polymerase in Mock Samples**
